% Author: liliff
% created: 2011.04.08
% modified: 2014.01.16

\documentclass{article}
% packages that come with TeXLive
\usepackage[letterpaper,margin=.75in,lmargin=1.5in,rmargin=.75in]{geometry}
\usepackage[sf,tiny,compact]{titlesec}
\usepackage{ifthen}
\usepackage{relsize}
\usepackage[pdfborderstyle={/S/U/W 0.5},allbordercolors={0.8 0 0}]{hyperref}
\usepackage{enumitem}
\setlist{nolistsep}
\urlstyle{same}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\labelitemi}{$\circ$}

\newcommand{\name}	{Musee Ullah}
\newcommand{\phone}	{1 408 686 9736}
\newcommand{\email}	{milkteafuzz@gmail.com}
\newcommand{\web}	{\url{milk.tea.jp}}
\newcommand{\location}	{Chicago, IL 60608}

\pagestyle{empty} % remove header/footer content (page numbers)
\setlength{\parindent}{0cm}
\setlength{\parskip}{0cm} % vertical space between paragraphs
\setcounter{secnumdepth}{0} % don't number sections

\newcommand{\sectionstyle}{\bfseries} % define font of sections 
\titleformat{\section}[leftmargin]{\titlerule*[0.2em]{\bfseries\_}%
  \vspace{4pt}\filleft}{\thesection}{5em}{\sectionstyle}
% The X can be replaced with any other character or string. It
% designs the "separator" before sections. Play with it.
% The characters | . _ - and * seem most desirable.
\titlespacing{\section}{0.8in}{1.5ex plus .1ex minus .2ex}{0.2in}
% First argument, width of the text space; second, vertical space
% above text; third, space between text and resume content

% this makes the title. various formatting stuff involved.
\newcommand{\makeheader}{%
  {\Large\bf\name}\hfill{}{\location\par}% name and location
  {\setlength{\baselineskip}{0in}\rule[-0.5mm]{\textwidth}{0.5pt}\par}%
  {\hspace{\stretch{3}}%
    web: \web\hspace{\stretch{1}}%
    email: \email\hspace{\stretch{1}}%
    phone: \texttt{+}\phone\hspace{0.5em}%
  }%
  \vspace{0.5em}%
}

% 1 2  <-Use this to define your schools, companies, and organisations.
\newenvironment{entity}[2]{%
    \textbf{#1}\hfill #2\par
}{
    \vspace{0.1em}%
    \par%
}
\newenvironment{position}[2]{%
    \ifthenelse{\not\equal{#1}{}\or\not\equal{#2}{}}{\textsl{#1}\hfill#2\par}
}{
    \vspace{0.3em}%
}

\begin{document}
\makeheader
\section{Objective}

An entry-level position in sysadmin/devops.
\section{Employment}

    \begin{entity}{\href{http://sleepygiant.com}{Sleepy Giant Entertainment}}{Chicago, IL}

        \begin{position}{Systems Engineer}{July 2013 and ongoing}

- Monitored game servers for outages, issues.\par
- Introduced to Chef and various devops workflow tools.\par
- Created a few internal scripts/tools, Dash for instance.\par


        \end{position}

    \end{entity}
    \begin{entity}{\href{http://hostgator.com}{HostGator.Com, LLC}}{Austin, TX}

        \begin{position}{Systems Administrator}{June 2011 to July 2012}

-- Primarily help desk support - dealt with issues like:\begin{itemize}
    \item PHP/MySQL/Rails/website/application errors and issues  
    \item Backups and restorations, using customer provided tarballs or rsync from NAS backup appliances  
    \item Reboot triage and server tuning (particularly MySQL/Percona and Apache)  
    \item Software upgrades and installations (Apache/PHP modules, Redmine, phpBB, etc.)  
\end{itemize}
-- Filed internal bug reports and wrote documentation for company wikis and knowledgebase.

        \end{position}
        \begin{position}{Systems Monitoring}{December 2011 to July 2012}

-- Monitored $>$4500 servers, using Zabbix (and ZMonitor), in a small team to maintain quality service.\par
-- A typical week consisted of:\par
\begin{itemize}
    \item Reducing abnormal load and user abuse (rogue scripts, spam, hacked accounts)  
    \item Checking and reporting hardware health (disk usage, filesystem status, drive swaps, RAID health)  
    \item Restoring network connectivity and deflecting attacks (UDP/SYN floods, Slowloris)  
    \item And correcting broken configurations (network, services).  
\end{itemize}
-- Wrote \href{http://forums.hostgator.com/search.php?do=finduser&u=126179}{public announcements} on the \href{http://forums.hostgator.com/network-status-f14.html}{network status forums} for extended downtime issues.\par
-- Assisted a Level 3 administrator in migrating the farm from 32bit to 64bit.

        \end{position}

    \end{entity}
    \begin{entity}{Contracted Positions}{}

-- \href{http://batee.com}{\textbf{batee.com}} - site redesign using bootstrap (by request); uses jekyll for site generation

    \end{entity}
\section{Volunteering}

-- \href{http://knightsofreason.net}{\textbf{Knights of Reason}} - primary contact for technical issues, server owner/co-admin, forum moderator. (\href{https://wiki.milkteafuzz.com}{server documentation})\par
-- \href{http://thebikeproject.org}{\textbf{The Bike Project of Urbana-Champaign}} (Urbana, IL, 8/2010-2/2011) - bike mechanic and technologist, e.g. repurposed old laptops with Debian for use at the shop.\par

\section{Projects / One-Offs}

-- \href{https://github.com/liliff/zmonitor}{\textbf{ZMonitor}} - cli dashboard for zabbix written in ruby\par
-- \href{https://github.com/liliff/wagnaria}{\textbf{Wagnaria}} - fansubbing organisation tool written in python and angularjs (\href{https://c.milkteafuzz.com/index.html}{copy of it in production})\par
-- \href{http://ip.milk.tea.jp}{\textbf{IP Lookup}} - single page app written in angularjs to map a geolocated IP\par
-- \textbf{Dash} - ruby/rack dashboard for nagios with angularjs frontend\par

\section{Familiarities / Preference}

\textbf{distros}: arch linux, centos, debian\par
\textbf{lang}: bash, ruby, python; markdown, json\par
\textbf{apps}: nginx, mysql, mongodb, etherpad, chef\par
\textbf{workflow}: git, vim, i3wm, remmina, vagrant, did I mention bash (scripts)?\par

\section{Education}

\textbf{University of Illinois at Urbana-Champaign} - 2010 -- 2011 - East Asian Languages and Cultures
\section{Links}

\textbf{Github:} \url{www.github.com/liliff}\par
\textbf{LinkedIn:} \url{www.linkedin.com/in/musee}
\\
\\
\textsl{Source:} \url{https://raw.github.com/liliff/resume/master/resume.md}
\end{document}
